---
title: "assignment"
author: "Justin Berg"
date: "2023-08-23"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(raster)
library(habtools)
library(ggplot2)
library(dplyr)
library(fishualize)

plot(horseshoe)
```

###Current lab: Nelson Lab
###Project focus: I will study runoff on the coral microbiome and metabolome, specfically in West Maui and possibly Guam. I also am aiding in the Donahue Lab nutrient experiment. 
###Why you chose this course: I wanted to learn new techniques about coral reef photogrametry that could be used in my future work with shifts in reefs that involce runoff. 
###What do you want to learn about the most in this course: I enter this class very open minded and hope to walk away with a better understanding of how others may approach certain coral related issues and to have an open dialogue about creative ways to approach my future research goals and objectives. 
###Your R experience: I have taken advanced statistics in R last fall and have been modeling and visualizing in R for the last 5 years. 
###Fun fact: I love cooking and eating new foods, so my girlfriend and I are cooking a meal from each country around the world (currently have about 12 done). 

